A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-14 docs/elsarticle/elsarticle-template.tex
paper

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of work steps directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. In turn, spatial AR is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear AR glasses. However, care must be taken to distort the images to be projected in a manner that they appear undistorted to the viewer, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene. For planar scene geometry (such as a floor, wall, or table), this can be done in a cumbersome manual process called keystone correction, often using software bundled with the projector.

@@

Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of work steps directly into the scene, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of AR glasses. Reliance on AR glasses has two adverse consequences: (i) AR glasses must be worn by each individual wishing to view the augmentation, and (ii) such glasses---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. Spatial AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with AR glasses, but by projection to the scene itself, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction, often using software bundled with the projector.

@@

The hardware setup employed in this work comprised a Panasonic XXX projector with a steerable mirror system manufactured by XX. In addition, we used a Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The setup was mounted on the ceiling of the Pilotfabrik, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. The floorspace used for our experiments measured dimensions of X~m~$\times$~Y~m; the projector was mounted at approximately the center of this space, at a height of ca.\ XX m.

@@

\paragraph{Camera 2D-3D correspondences}

\paragraph{Projector 2D-3D correspondences}

\subsection{Distortion}

@@

\begin{equation}
\mathtt{H} = \mathtt{K}_\text{proj}\left(\mathtt{R}' + \frac{1}{Z^{} \mathbf{n}^\top \mathbf{p}^{}}\mathbf{t}'\mathbf{n}^\top\right)\mathtt{K}_\text{proj}^{-1},
\label{homgen}
\end{equation}
where ()

>>>>

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of work step instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. In turn, spatial AR is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear AR glasses. However, care must be taken to distort the images to be projected in a manner that they appear undistorted to the viewer, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene. For planar scene geometry (such as a floor, wall, or table), this can be done in a cumbersome manual process called keystone correction, often using software bundled with the projector.

@@

Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of work step instructions directly into the scene, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of AR glasses. Reliance on AR glasses has two adverse consequences: (i) AR glasses must be worn by each individual wishing to view the augmentation, and (ii) such glasses---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. Spatial AR is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with AR glasses, but by projection to the scene itself, thus eliminating both aforementioned problems. Yet considering for the moment a planar surface to be augmented, unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction, often using software bundled with the projector.

@@

The hardware setup employed in this work comprised a Panasonic PT-RZ660BE projector with a steerable mirror system manufactured by Dynamic Projection Institute. In addition, we used a Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The setup was mounted on the ceiling of the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. The floorspace used for our experiments measured dimensions of X~m~$\times$~Y~m; the projector was mounted at approximately the center of this space, at a height of ca.\ XX m.

@@

\paragraph{Camera calibration}

\paragraph{Projector calibration}

The pose of the projector is given in the coordinate frame of the camera.

\subsection{Correcting for Distortion}

@@

\begin{equation}
\mathtt{H} = \mathtt{K}_\text{proj}\left(\mathtt{R}' - \frac{\mathbf{t}'\mathbf{n}^\top}{d}\right)\mathtt{K}_\text{proj}^{-1},
\label{homgen}
\end{equation}
where $(\mathbf{n}^\top, -d)^\top$ gives the scene plane and $d = \mathbf{n}^\top\mathbf{X}$, for any point $\mathbf{X}$ in the plane.
